A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-31 doc/large_strain.tex
Finish basic outline of sec 3.

In practise this implies that parallelization of the assembly operation (for the matrix-based approach) and the linear solver (as well as various pre- and post-processing steps), both of which are the focal points of discussion in this manuscript, has been achieved using MPI.

The results of the matrix-free approach with a geometric-multigrid preconditioner are compared to the matrix-based approach in conjunction with the algebraic multigrid (AMG) preconditioner using the package ML of the Trilinos \cite{Heroux2005} library, version 12.12.1.

>>>>

In practise this implies that parallelization of the assembly operation (for the matrix-based approach) and the linear solver (as well as various pre- and post-processing steps), both of which are the focal points of investigation in this manuscript, has been achieved using MPI.
For the linear solver, \texttt{deal.II}'s implementation of the preconditioned conjugate gradient (CG) solver for symmetric positive-definite systems is consistently used, leaving the choice for method of assembly and linear system preconditioning remaining.
For the matrix-based approach, the Trilinos \cite{Heroux2005} library, version 12.12.1 was leveraged; 
the system tangent matrix is stored in a distributed \textit{Epetra\_FECrsMatrix} from the Epetra package \cite{Heroux2005b} sparse data structure and the linear solver was preconditioned with an algebraic multigrid (AMG) preconditioner from the package ML package \cite{Gee2006a}.
The second implementation, which is discussed in detail in the following Sections, utilized a matrix-free approach in conjunction with a geometric-multigrid preconditioner.
